Think deep for reef resilience

### 2025-08-07 paper/paper_draft.qmd
Move GBR-wide DHW figure to methods section and move DHW clustered-results figure to supplementary

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and GCM
development families. The IPCC defines ECS as the long term warming caused by a doubling of
carbon dioxide above its pre-industrial concentration [@forster2021]. The five GCMs
therefore allow for a range of possible climate futures to be explored, capturing the
uncertainty in future responses to CO2 increases (@sfig-ecs; @sfig-methods-dhws;
[@grose2023; @shepherd2018]).

@@

@@

Under each GCM, in all management areas, low, medium and high cluster reefs have low
differences between DHW trajectories (@fig-gcm-dhw-trajectories) \[**TI:** **I don't
understand this sentence - what is meant by reefs have low differences?**\]. The highest
peak DHW levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in
overall DHW timeseries occur under ACCESS-CM2.

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
represented five times (for each GCM), with each GCM displayed
horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
width="14.82cm"}

@@

![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
the different management areas across the Great Barrier Reef. Green represents
Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
represents the Townsville-Whitsunday management area. Solid lines represent the
management-area median timeseries and bands represent the 2.5 to 97.5 percentile confidence
intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#sfig-methods-dhws
width="14.82cm"}

@@

![Heatmaps indicating reef connectivity relative standard deviation (RSD %). Reef
connectivity relative standard deviation represents the reef standard deviation connection
strength as a percentage of reef mean connection strength. Lighter colours indicate higher
RSD %
values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
width="14.82cm"}

>>>>

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and GCM
development families. The IPCC defines ECS as the long term warming caused by a doubling of
carbon dioxide above its pre-industrial concentration [@forster2021]. The five GCMs
therefore allow for a range of possible climate futures to be explored, capturing the
uncertainty in future responses to CO2 increases (@sfig-ecs; @fig-methods-dhws;
[@grose2023; @shepherd2018]).

@@

![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
the different management areas across the Great Barrier Reef. Green represents
Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
represents the Townsville-Whitsunday management area. Solid lines represent the
management-area median timeseries and bands represent the 2.5 to 97.5 percentile confidence
intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
width="14.82cm"}

@@

Under each GCM, in all management areas, low, medium and high cluster reefs have low
differences between DHW trajectories (@sfig-gcm-dhw-trajectories) \[**TI:** **I don't
understand this sentence - what is meant by reefs have low differences?**\]. The highest
peak DHW levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in
overall DHW timeseries occur under ACCESS-CM2.

@@

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
represented five times (for each GCM), with each GCM displayed
horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
width="14.82cm"}

@@

![Heatmap indicating reef connectivity relative standard deviation (RSD %). Reef
connectivity relative standard deviation represents the reef standard deviation connection
strength as a percentage of reef mean connection strength. Lighter colours indicate higher
RSD %
values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
width="14.82cm"}
